\chapter*{Acknowledgments}
%I would like to thank...

The research described in this thesis as well as my growth as a scientist throughout graduate school has come about from the guidance and mentorship from many. To express my gratitude towards them with these small words is incredibly unfair. Nonetheless, they must be acknowledged.

Firstly, I am extremely grateful of my thesis advisor, Nadia Fomin, for giving me the opportunity to undertake PhD research in her group. She has been an excellent mentor and always provided me with the best guidance and support. Vince Cianciolo, has been like a second advisor to me. I've learned a tremendous amount from him while working together on the nEDM@SNS experiment. Thank you Vince for asking me thoughtful questions as well as answering all of my questions thoughtfully. I also appreciate both Nadia and Vince for reading this thesis and providing me critical feedback.

Additionally, I would like to thank Geoff Greene, for teaching me about neutrons and spin precession, and Seppo Penttila, for sharing with me his expertise on everything hardware related. Josh Pierce supplied his experienced input on the development and analysis of the neutron polarimetry experiment. Thank you Josh for your numerous helpful insights and suggestions. I especially thank Peter Jiang for letting me work in his lab to develop the spin flipper as well as the in situ $^3$He SEOP system and for teaching me the intricacies of polarized $^3$He. My thesis experiment would not have been possible without the engineering support from John Ramsey and Isaiah Wallace. Thank you both for your work. I would like to thank Ricky Huffstetler and his physics machine shop team for fabricating the equipment used for my experiment. I'm also indebted to my collaborators from Caltech for commissioning the cryomagnet for the P/T experiment. Thank you Brad Filippone, Alina Aleksandrova, Marie Blatnik, Raymond Tat, Alston Croley and Wanchun Wei. Additionally, I would like to thank Brad Filippone for his guidance on the polarimetry analysis as well. Next, I would like to thank all of the Univ. of Tenn. neutron physics group members over the years for the camaraderie. Big shout out to Jordan O'Kronley for assisting me with the data taking.

Many ORNL neutron scientists supported my experiment. I would like to thank Matt Frost for assisting with the flux measurements and the neutron beam imaging. I thank Erik Iverson and Franz Gallmeier for the neutronics support. I would like to thank Kevin Berry and Loren Funk for letting me use their neutron detector and helping me troubleshooting it. Thank you Lisa Debeer-Schmitt for letting us perform beam window SANS studies at HFIR GP-SANS. Thank you Andre Parizzi \& Xiaosong Geng for helping out with repairing the monochromator. Thank you Bogdan Vacaliuc for servicing the DAS. I would also like to thank the SNS technicians, who provided the much needed support to install the infrastructure of the experiment.

Lastly, on a personal note, I'm grateful for my family; my parents for making sacrifices to ensure their children have a better future and my brother and sister for being my collaborators in fun and mischief.
 
The work presented in this dissertation was in part supported by U.S. D.O.E award number DE-FG02-03ER41258 and D.O.E Office of Science, WDTS-SCGSR program under contract number DE‐SC0014664.